A molecular taxonomy of tumors independent of tissue-of-origin

### 2020-08-15 text/fig_legend.Rmd

**Figure 7: **

>>>>

**Figure 7: ** Comparison of different cancers, simulated and actual
results results. A) To understand the risk model, we plot survival of
four simulated cohorts. Compare survival of a group consisting of
randomly selected 30 year old women (light blue) to an equal sized
group of 30 year old women with cancer, k = 2 (light orange). To
understand how the mix of ages alters the survival curve, we compare a
randomly selected group of people with ages uniformly distributed from
30 to 70 (dark blue) and a randomly selected group with uniformly
distributed ages and cancer k = 2 (dark orange). B,C,D,E) We compare a
randomly selected group with correct age distribution for the given
cancer (blue) to the model predicted survival for the given average k
(red) and the actual survival for the patients in our dataset (CHOOSE
COLOR HERE, NOT GREEN). As can be seen, Stomach Cancer (STAD),
Glioblastoma (GBM), and Pancreatic Cancer (PAAD) are all very
deadly. The modeled results fit the general trend for the actual
patients. Thyroid Cancer (THCA) on the other hand has very little if
any effect on life expectancy, in fact there may be a slight benefit
which may be associated with a bias in diagnosis towards patients who
are more health conscious, or higher socioeconomic status, with more
access to care compared to random population members.

**Figure 8** Tissue specific effects are compared by showing the
probability density for the posterior value of the k_tis
multiplier. These values reflect the general deadliness of the cancer
type across all clusters. GBM, PAAD, and SKCM stand out as having
values in the 10 to 20 range with a wide degree of uncertainty. Other
cancers such as Prostate (PRAD) and Thyroid (THCA) show values down
near or even below 1 suggesting that these populations may have
healthier lifestyles and more access to care. Most cancer types fall
in the range 2-7 as might be expected.

**Figure 9** Class specific $k_class$ values shown for each cancer
type. The overall $k$ value is the product of $k_tis \times
k_class$. The class specific value shows the relative aggressiveness
of that particular class within the tissue. For example class 1, 2,
and 6 Glioblastoma (GBM) are apparently much less deadly than other
types of GBM. A similar situation can be seen with Pancreatic Cancer
(PAAD) where 1, 6, and 8 are less deadly compared to classes 7,
9, 10. For some cancer types there are few data points and little
ability to estimate values with precision (DLBC and KICH for example).
